\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
evaluation-figs

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

@@

\begin{figure}
\centering
\subfigure[Satisfied BA demands]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/test.pdf}}
\subfigure[Failures of links]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/link-failures.pdf}}
%\subfigure[Scheduled results (SWAN)]{
%\includegraphics[width=0.19\textwidth]{fig/testbed6.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Data loss ratio]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/data-loss.pdf}}
%%\subfigure[After L4 failure ($\mathsf{BATE}$-1)]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/time2.pdf}}
%\subfigure[Events after L3 failure]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/fake-failure.pdf}}
\caption{A simple example with three parallel demands.}
\label{e1}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[\mathsf{BATE} v.s. other TE algorithms]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\caption{BA satisfaction results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

\textbf{Evaluation results.}
\begin{figure}[h]
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second.

\begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}

@@

\begin{figure} 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

>>>>

 \begin{figure}[t]
\begin{center}
\includegraphics [width=0.68\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

@@

\begin{figure}
\centering
\subfigure[Satisfied BA demands]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/test.pdf}}
\subfigure[Failures of links]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/link-failures.pdf}}
%\subfigure[Scheduled results (SWAN)]{
%\includegraphics[width=0.19\textwidth]{fig/testbed6.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Measured bandwidth (DC1 to DC3)]{
%\includegraphics[width=0.19\textwidth]{fig/evaluation/fake/throughput.pdf}}
%\subfigure[Data loss ratio]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/data-loss.pdf}}
%%\subfigure[After L4 failure ($\mathsf{BATE}$-1)]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/time2.pdf}}
%\subfigure[Events after L3 failure]{
%\includegraphics[width=0.24\textwidth]{fig/evaluation/fake-failure.pdf}}
\caption{An example with three parallel demands.}
\label{e1}
\end{figure}

@@

\begin{figure}[t]
\centering
\subfigure[$\mathsf{BATE}$ v.s. other TE algorithms]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/no-fixed.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\caption{BA satisfaction results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

\textbf{Evaluation results.}
\begin{figure}[t]
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second. 
%
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
%\caption{Profit gain after failures}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

\begin{figure}[t]
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}
